### 2021-06-09 paper/report.tex
Add references and solve comments.

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd
immunity.\comment[id=HM]{Cite some paper on herd immunity, maybe vaccine data} In the
meantime, it is of utmost importance to employ an effective mix of strategies for
containing the virus. The most frequent initial response was a set of non-pharmaceutical
interventions (NPIs) to reduce contacts between individuals. While this has allowed some
countries to sustain equilibria with very low infection numbers\footnote{See
    \citet{Contreras2021} for a theoretical equilibrium at low case numbers which is
    sustained with test-trace-and-isolate policies.}, most have seen large fluctuations of
infection rates. Containment measures have become increasingly diverse and now include
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or more infectious virus strains are well understood in
quantitative terms. This paper develops a model incorporating all these factors. The
framework allows to combine a wide variety of data in a timely fashion, making it useful
to predict the effects of various interventions. We apply the model to Germany and show
that rapid testing had the largest impact on the reduction in infections by almost 80\%
during the month of May 2021. We conclude that rapid tests have a large role to play at
least as long as vaccinations have not been offered to an entire population.

@@

In our model, susceptibility to contracting the SARS-CoV-2 virus is dependent on
age. A possible infection progresses as shown in
Figure~\ref{fig:disease_progression}. We differentiate between an initial period
of infection without being infectious or showing symptoms, being infectious
(presymptomatic or asymptomatic), showing symptoms, requiring intensive care,
and recovery or death.\comment[id=HM]{Seems broadly standard, can we cite
someone?} The probabilities of transitioning between these states depend on age;
their duration is random within intervals calibrated to medical literature (for
a detailed description see Section~\ref{sec:medical_params}). Conditional on the
type of contact, infectiousness is independent of age \citep{Jones2021}.

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data/RKI} We model the
period mid-September 2020 to the end of May 2021. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) Second, a large fraction cases
during summer of 2020 were traced to international travel
\citep{KochInstitut2021,Hodcroft2021} but the precise number is difficult to model.

>>>>

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many months---and
often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=K]{WHO Press Conference saying we won't reach herd
immunity in 2021} In the meantime, it is of utmost importance to employ an effective mix
of strategies for containing the virus. The most frequent initial response was a set of
non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While
this has allowed some countries to sustain equilibria with very low infection
numbers\footnote{See \citet{Contreras2021} for a theoretical equilibrium at low case
numbers which is sustained with test-trace-and-isolate policies.}, most have seen large
fluctuations of infection rates. Containment measures have become increasingly diverse
and now include testing, more nuanced NPIs, and contact tracing. Neither these policies'
effect nor the influence of seasonal patterns or more infectious virus strains are well
understood in quantitative terms. This paper develops a model incorporating all these
factors. The framework allows to combine a wide variety of data in a timely fashion,
making it useful to predict the effects of various interventions. We apply the model to
Germany and show that rapid testing had the largest impact on the reduction in infections
by almost 80\% during the month of May 2021. We conclude that rapid tests have a large
role to play at least as long as vaccinations have not been offered to an entire
population.

@@

In our model, susceptibility to contracting the SARS-CoV-2 virus is dependent on age. A
possible infection progresses as shown in Figure~\ref{fig:disease_progression}. We
differentiate between an initial period of infection without being infectious or showing
symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring
intensive care, and recovery or death as for example also modeled in \cite{Grimm2021}.
The probabilities of transitioning between these states depend on age; their duration is
random within intervals calibrated to medical literature (for a detailed description see
Section~\ref{sec:medical_params}). Conditional on the type of contact, infectiousness is
independent of age \citep{Jones2021}.

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between May and mid-September, daily new infections
were below 20 per Million and day \citep{MaxRoser2020}. We model the
period mid-September 2020 to the end of May 2021. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) Second, a large fraction cases
during summer of 2020 were traced to international travel
\citep{KochInstitut2021,Hodcroft2021} but the precise number is difficult to model.
